### 2019-05-09 paper-three/paper-three.tex
added sense door diagram

\usepackage{enumitem}

@@

\Huge\textbf{Every experience which emerges in the mind, whether a thought or emotion, always surfaces
with a corresponding sensation on the body.}

@@

TODO: sense circle diagram

5 Senses by Daniel Falk from the Noun Project: https://thenounproject.com/daniel2021/collection/human-body-senses/
Thought by Nociconist from the Noun Project: https://thenounproject.com/search/?q=thought&i=2025873
Heart by Rafael Garcia Motta from the Noun Project: https://thenounproject.com/search/?q=heart&i=807960
Body by Makarenko Andrey from the Noun Project: https://thenounproject.com/search/?q=body&i=789989

@@

>>>>

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{enumitem}
\usepackage{hyperref}

@@

\vspace{1cm}
\textbf{Every experience which emerges in the mind, whether a thought, emotion, or contact of the five senses, always surfaces with a corresponding sensation on the body.}
\vspace{1cm}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=11cm]{images/sense-doors.png}
  \caption{The sense doors and bodily sensation.}
  \label{fig:sense-doors}
\end{figure}

The totality of human experience can be categorized according to the ``sense doors''
listed in Figure~\ref{fig:sense-doors} \cite{sense-icons}: The five external sense doors of sight, sound,
taste, smell, and touch are listed at the top. The internal sense door of ``mind'' is
broken down into thought and emotion, second to the bottom. At the very bottom of the
diagram is bodily sensation, the object of meditation in Vipassana.

Once these eight experiences are listed, there is no experience left undescribed. All
human experience from the mundane (imagination, daydreaming, physical pleasures,
physical discomforts, etc.) to the supramundane (out-of-body experiences,
hallucinations, etc.) are subsets of these seven sense doors and their reflection in
bodily sensation, the eighth.

TODO: Attention in one place only

@@

\begin{thebibliography}{9}
\raggedright

\bibitem{sense-icons}
  5 Senses by Daniel Falk from the Noun Project
  \url{https://thenounproject.com/daniel2021/collection/human-body-senses/}
  Thought by Nociconist from the Noun Project
  \url{https://thenounproject.com/search/?q=thought&i=2025873}
  Heart by Rafael Garcia Motta from the Noun Project
  \url{https://thenounproject.com/search/?q=heart&i=807960}
  Body by Makarenko Andrey from the Noun Project
  \url{https://thenounproject.com/search/?q=body&i=789989}
  \textit{The Noun Project}.

\end{thebibliography}
